Resolving Limits Faced by Classical Machine Learning Approaches: Areas of Application for Collaborative Interactive Learning Techniques

### 2018-08-11 paper.tex
Reintroduce abbreviations in first section

% As a general rule, do not put math, special symbols or citations
% in the abstract
\begin{abstract}
The area of \textit{Machine Learning (ML)} has experienced a high 
level of research interest in the last few years with it's underlying 
theory reaching back far into the 18th century. Due to minimal 
costs for computation and the massive availability of data in the 
Internet recent research interest has been mainly focused on 
\textit{automatic ML (aML)}. In this ML paradigm a model 
(e.g.\ classifier, \dots) is being trained with a pre-labeled training 
set in order to make predictions on unknown unlabeled data. Problems arise 
in domains where data is rarely available or where the labeling process is 
too expensive (computationally or economically). Furthermore, real-world data 
can be uncertain, incomplete or contain noisy data. In these cases 
full automation is not reliable enough or even infeasible for specific 
domains. However, robust and trustworthy results are mandatory in a lot of 
applications like health informatics or autonomous vehicles. 
Therefore, systems are needed that interactively integrate knowledge from 
various experts, which can be collaborating humans or machines, in order 
to continuously improve results over a system's whole lifetime: So called 
\textit{Collaborative Interactive Learning (CIL)} systems.
This paper contributes in presenting an overview of classical ML approaches 
in comparison with CIL and outlines possible areas of application. 
\end{abstract}

@@

\notes{[Introduce abbreviations again.]}

@@

definition for the term \textit{Machine Learning} but at its most basic form it 

@@

    \item \textit{Image recognition, OCR}.

>>>>

% As a general rule, do not put math, special symbols or citations
% in the abstract
\begin{abstract}
The area of \textit{Machine Learning} has experienced a high 
level of research interest in the last few years with it's underlying 
theory reaching back far into the 18th century. Due to minimal 
costs for computation and the massive availability of data in the 
Internet recent research interest has been mainly focused on 
\textit{Automatic Machine Learning}. In this paradigm a model 
(e.g.\ classifier, \dots) is being trained with a pre-labeled training 
set in order to make predictions on unknown unlabeled data. Problems arise 
in domains where data is rarely available or where the labeling process is 
too expensive (computationally or economically). Furthermore, real-world data 
can be uncertain, incomplete or contain noisy data. In these cases 
full automation is not reliable enough or even infeasible for specific 
domains. However, robust and trustworthy results are mandatory in a lot of 
applications like health informatics or autonomous vehicles. 
Therefore, systems are needed that interactively integrate knowledge from 
various experts, which can be collaborating humans or machines, in order 
to continuously improve results over a system's whole lifetime: So called 
\textit{Collaborative Interactive Learning (CIL)} systems.
This paper contributes in presenting an overview of classical Machine Learning 
approaches in comparison with CIL and outlines possible areas of application. 
\end{abstract}

@@

@@

definition for the term \textit{Machine Learning (ML)} but at its most basic form it 

@@

    \item \textit{Image recognition, Optical Character Recognition (OCR)}.
